\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-25 paper/main.tex
updates to abstract

  Reproducibility is a core requirement of modern scientific research.
  For computational research, reproducibility means that code should
  produce the same results, even when run on different systems.  A
  standard approach to ensuring reproducibility entails packaging a
  project's dependencies along with its primary code base.  Existing
  solutions vary in how deeply these dependencies are specified,
  ranging from virtual environments, to containers, to virtual
  machines.  Each of these existing solutions requires installing or
  setting up a system for running the desired code that must be
  packaged alongside the primary code base.  Here we propose a
  lighter-weight solution than virtual environments: the
  \texttt{davos} library.  When used in combination with a
  notebook-based Python project, the \texttt{davos} library provides a
  mechanism for specifying (and automatically installing) the correct
  package versions of the project's dependencies.  The \texttt{davos}
  library also ensures that those versions are in use any time the
  notebook's code is executed.  This enables researchers to share a complete
  reproducible copy of their code within a single Jupyter notebook file.

>>>>

  Reproducibility is a core requirement of modern scientific research.
  For computational research, reproducibility means that code should
  produce the same results, even when run on different systems.  A
  standard approach to ensuring reproducibility entails packaging a
  project's dependencies along with its primary code base.  Existing
  solutions vary in how deeply these dependencies are specified,
  ranging from virtual environments, to containers, to virtual
  machines.  Each of these existing solutions requires installing or
  setting up a system for running the desired code, increasing the 
  complexity and time cost of sharing or engaging with reproducible 
  science. Here, we propose a lighter-weight solution:  the
  \texttt{davos} library.  When used in combination with a
  notebook-based Python project, the \texttt{davos} library provides a
  mechanism for specifying (and automatically installing) the correct
  versions of the project's dependencies.  The \texttt{davos}
  library further ensures that those packages and specific versions are used every time the
  notebook's code is executed.  This enables researchers to share a complete
  reproducible copy of their code within a single Jupyter notebook file.
